Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
figure

Figure \ref{fig:main_results} shows the predictive performance of HSLDA 
relative to the three comparison models. In figure \ref{fig:1b}.

\begin{figure}%[htbp]
\begin{center}
%\subfloat[][\label{fig:1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:1b}\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%\subfloat[][\label{fig:1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
\subfigure[][]{\label{fig:1d}\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\caption{Out-of-sample ICD-9 code prediction from patient free-text discharge records 
(\subref{1a} and \subref{fig:1b}). Out-of-sample Amazon product category predictions from 
product free-text descriptions (\subref{1c} and \subref{fig:1d}). In all figures, solid is 
HSLDA, dashed are independent regressors + sLDA (hierarchical 
constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
tree-conditional regressions. \subref{} and \subref{} show predictive performance as a function of the 
auxiliary variable threshold and \subref{fig:1b} and \subref{fig:1d} show predictive perfmance as a function of the
prior mean on regression coefficients.}
\label{fig:main_results}
\end{center}
\end{figure}

%\begin{figure}[t]
%\centering
%\parbox{0.9\columnwidth}{
% \vspace*{-\subfigtopskip}
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.01\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0155626\\
%         \mbox{~~~~~~}LEX: new acute myocardial infarction\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0520887\\
%         \mbox{~~~~~~}LEX: ST-segment depression
%       }}}
% }\goodgap
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.02\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0155626\\
%         \mbox{~~~~~~}LEX: new acute myocardial infarction\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0002962\\
%         \mbox{~~~~~~}LEX: prior angina%
%       }}}
% }\\     \vspace*{-\subfigtopskip}
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.03\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0011065\\
%         \mbox{~~~~~~}LEX: death\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0520887\\
%         \mbox{~~~~~~}LEX: ST-segment depression%
%       }}}
% }\goodgap
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.04\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0011065\\
%         \mbox{~~~~~~}LEX: death\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0002962\\
%         \mbox{~~~~~~}LEX: prior angina%
%       }}}
% }}
%\caption{A Content Item after atomization.}\label{fig:org-afteratom}
%\end{figure}

>>>>

Figure \ref{fig:main_results} shows the predictive performance of HSLDA 
relative to the three comparison models as a function of the prior mean
on regression coefficient. Figure \ref{fig:1a} demo.

\begin{figure}%[htbp]
\begin{center}
%\subfloat[][\label{fig:1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:1a}\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%\subfloat[][\label{fig:1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
\subfigure[][]{\label{fig:1b}\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\caption{Out-of-sample ICD-9 code prediction from patient free-text discharge records 
(\subref{fig:1b}). Out-of-sample Amazon product category predictions from 
product free-text descriptions (\subref{fig:1b}). In both figures, solid is 
HSLDA, dashed are independent regressors + sLDA (hierarchical 
constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
tree-conditional regressions.}
\label{fig:main_results}
\end{center}
\end{figure}

\begin{figure}[t]
%tbp] %  figure placement: here, top, bottom, or page
 \centering \includegraphics[scale=0.4]{figs/ROC_comparison_leafs} \caption{ROC Curve for clinical data}
